---
title: "p8105_hw1_mm5354"
author: "Mengran Ma"
date: "2018/9/13"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
#Problem 1

Here's a **code chunk** that samples from 
a _uniform distribution_:

```{r uniform_sample}
sample = runif(10, min=0, max=5)
```
I can take the mean of the sample, too!
The mean is `r mean(sample)`.

Next, creating the following required vectors:
A logical vector indicating whether elements of the sample are greater than 2
A (length-10) character vector
A (length-10) factor vector

```{r vectors}
example_df = tibble(
  vector_logical = c(sample > 2),
  vector_char = c(length(10)),
  vector_factor = factor(10)
)

class(example_df$vec_logical)
class(example_df$vec_char)
class(example_df$vec_factor)
```
For each vector, get the means:
Here is the mean for logical vector: `r mean(vec_logical)`
Here is the mean for character vector: `r mean(vec_char)`
Here is the mean for factor vector: `r mean(vec_factor)`


