---
title: "p8105_hw1_mm5354"
author: "Mengran Ma"
date: "2018/9/13"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Problem 1

```{r include = FALSE}
library(tidyverse)
```


Here's a **code chunk** that samples from 
a _uniform distribution_:

```{r uniform_sample}
sample = runif(10, min = 0, max = 5)
```
I can take the mean of the sample, too!
The mean is `r mean(sample)`.

Next, creating the following required vectors:
1. A logical vector indicating whether elements of the sample are greater than 2
2. A (length-10) character vector
3. A (length-10) factor vector

```{r vectors}
vec_logical = sample > 2
vec_char = c("Kao","Shi","Xin","Chun","Ge","Yong","Yuan","Bu","Gua","Ke")
vec_factor = factor(c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"))
```


For each vector, get the means:
Here is the mean for logical vector: `r mean(vec_logical)`

Here is the mean for character vector: `r mean(vec_char)`

Here is the mean for factor vector: `r mean(vec_factor)`

Write a code chunk that applies the as.numeric function to the logical, character, and factor variables
```{r as_numeric}
convert_veclog = as.numeric(vec_logical)
convert_vecchar = as.numeric(vec_char)
convert_vecfact = as.numeric(vec_factor)
```

What happens?

My answer is: Logical, and factor variables can be converted to numeric vectors, while in contrast, character variable/vector can not be converted to numeric vector. "NA" occurs in this converting character to numeric process.


In a second code chunk, convert your character variable from character to factor to numeric; similarly, convert your factor variable from factor to character to numeric. 

```{r convertions}
facconvert_vecchar = as.factor(vec_char)
numconvert_vecchar = as.numeric(facconvert_vecchar)

charconvert_vecfac = as.character(vec_factor)
numconvert_vecfac = as.numeric(charconvert_vecfac)
```


What happens?

My answer is: Character variable to factor to numeric can be converted/proceed successfully; However, converting factor variable to character to numeric did not work well comparing to the process above, since "NA" appears in this process when checking the numeric results.


#Problem 2

Create a data frame comprised of:
x: a random sample of size 1000 from a standard Normal distribution
```{r generating_x}
set.seed(2)

x = rnorm(1000, sd = 1)


```
y: a random sample of size 1000 from a standard Normal distribution
```{r generating_y}
set.seed(2)

y = rnorm(1000, sd = 1)
```
A logical vector indicating whether the x + y > 0
```{r checking_xy}
veclogical_checkxy = x + y > 0
```


A numeric vector created by coercing the above logical vector
```{r numvec_convert_logvec}
numvec_checkxy = as.numeric(veclogical_checkxy)
```

A factor vector created by coercing the above logical vector
```{r facvec_convert_logvec}
facvec_checkxy = as.factor(veclogical_checkxy)
```


* The size of the dataset is `r table(veclogical_checkxy)`.

* The mean of x is `r mean(x)`.

* The median of x is `r median(x)`.

* The proportion of cases for which the logical vector is TRUE equals to `r table(veclogical_checkxy) ["TRUE"]`.



Make a scatterplot of y vs x
```{r scatter_plot}
set.seed(2)

## define data frame containing x and y
plot_df = tibble(
  x = rnorm(1000, sd = 1),
  y = rnorm(1000, sd = 1)
)
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```
```{r scatter_plot2}
ggplot(plot_df, aes(x = x, y = c(facvec_checkxy),color = 'pink')) + geom_point()
```

```{r scatter_plot3}
ggplot(plot_df, aes(x = x, y = c(numvec_checkxy),color = 'blue')) + geom_point()
```