---
title: "p8105_hw1_mm5354"
author: "Mengran Ma"
date: "2018/9/13"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Problem 1

```{r include = FALSE}
library(tidyverse)
```


Creating the following required vectors:
1. A random sample of size 10 from a uniform[0, 5] distribution
2. A logical vector indicating whether elements of the sample are greater than 2
3. A (length-10) character vector
4. A (length-10) factor vector

```{r vectors}
set.seed(1)
problem1_df = tibble(
  sample = runif(10, min = 0, max = 5),
  vec_logical = sample > 2,
  vec_char = c("Kao","Shi","Xin","Chun","Ge","Yong","Yuan","Bu","Gua","Ke"),
  vec_factor = factor(c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"))
)
```


For each vector, get the means:

```{r get_means}
#Here is the mean of the sample
mean(problem1_df$sample)

#Here is the mean for logical vector
mean(problem1_df$vec_logical)

#Here is the mean for character vector
mean(problem1_df$vec_char)

#Here is the mean for factor vector
mean(problem1_df$vec_factor)

```
From the above, I tried to take the mean of each variable in my dataframe. What works and what doesn’t? My answer to this question: Only for numeric and logical vectors, we can obtain means using "mean()" this function, but not for character and factor vectors. Note that logical vectors use "1" to denote TRUE, and "0" to denote FALSE, therefore can produce mean value.


Write a code chunk that applies the as.numeric function to the logical, character, and factor variables
```{r as_numeric, eval = FALSE}
as.numeric(problem1_df$vec_logical)
as.numeric(problem1_df$vec_char)
as.numeric(problem1_df$vec_factor)
```

What happens?

My answer is: Logical, and factor variables can be converted to numeric vectors, while in contrast, character variable/vector can not be converted to numeric vector. "NA" occurs in this converting character to numeric process. Note that logical vectors use "1" to denote TRUE, and "0" to denote FALSE, therefore can be converted to numerics. For factor vector, R assigns each element with order number based on levels of factors, for here R assigns numerics to each level in alphebatic order.





In a second code chunk, convert your character variable from character to factor to numeric; similarly, convert your factor variable from factor to character to numeric. 

```{r convertions}
#convert your character variable from character to factor to numeric
facconvert_vecchar = as.factor(problem1_df$vec_char)
facconvert_vecchar

as.numeric(facconvert_vecchar)


#convert your factor variable from factor to character to numeric
charconvert_vecfac = as.character(problem1_df$vec_factor)
charconvert_vecfac

as.numeric(charconvert_vecfac)

```

What happens?

My answer is: Character variable to factor to numeric can be converted/proceed successfully: Character vector can be coerced into factor vector, as the levels are because of the alphabetic order of elements in those inputting characters. The coerced factor vector from 1 (to 10 in this question) can be converted to numerical vector, in which the numerics have been assigned to each level of factor following low to high alphebatical order; 
However, converting factor variable to character to numeric did not work as well as the process above: Factor vector can be converted to characters explicitly, but "NA" appears in the process when characters cannot be coerced into numerics.


#Problem 2

Create a data frame comprised of:
1. x: a random sample of size 1000 from a standard Normal distribution.
2. y: a random sample of size 1000 from a standard Normal distribution.
3. A logical vector indicating whether the x + y > 0.
4. A numeric vector created by coercing the above logical vector.
5. A factor vector created by coercing the above logical vector.

```{r generating_vectors}
set.seed(2)
problem2_df = tibble(
  x = rnorm(1000, sd = 1),
  y = rnorm(1000, sd = 1),
  veclogical_checkxy = x + y > 0,
  numvec_checkxy = as.numeric(veclogical_checkxy),
  facvec_checkxy = as.factor(veclogical_checkxy)
)
```


* The size of the dataset is `r nrow(problem2_df)` rows and `r ncol(problem2_df)` columns.

* The mean of x is `r mean(problem2_df$x)`.

* The median of x is `r median(problem2_df$x)`.

* The proportion of cases for which the logical vector is TRUE equals to `r table(problem2_df$veclogical_checkxy) ["TRUE"]/length(problem2_df$veclogical_checkxy)`.



Then, I made a scatterplot of y vs x, and colored points using the logical variable.
```{r scatter_plot}

ggplot(problem2_df, aes(x = x, y = y, color = veclogical_checkxy)) + geom_point()
ggsave("scatter_plot.pdf")
```
Here for this scatterplot, coloring points using the logical variable helps us to clearly identify which points give "TRUE" and which points give "FALSE" in logical vector x + y > 0. Because x and y are random variables generated from standard normal distribution, therefore we should observe that approximately half of the points will be evaluated to be TRUE and half to be FALSE.


Made a second scatterplot that color points using the factor variable.
```{r scatter_plot2}
ggplot(problem2_df, aes(x = x, y = y, color = facvec_checkxy)) + geom_point()
```

Made a third scatterplot that color points using the numeric variable.
```{r scatter_plot3}
ggplot(problem2_df, aes(x = x, y = y, color = numvec_checkxy)) + geom_point()
```

Here for the second and the third scatterplot, coloring points using the factor and numeric variables, respectively also helps us to clearly identify differentitations within the dataset/points. Since the numeric and the factor vector have all been created by coercing the above logical vector x + y > 0, we would see exactly the same two divisions' pattern as logical vector for both factor and numeric vectors. We could see a numerical scale by the side of plot, in which light blue color indicates larger values whereas dark black color indicates smaller values. In this numerical variable, we only have 0 or 1 these two divisions. Thus, we saw two discrete colors on the plot. Similarly, factor vector also only has two divisions, therefore points have been separated by two different colors.
