---
title: "p8105_hw1_mm5354"
author: "Mengran Ma"
date: "2018/9/13"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Problem 1

```{r include = FALSE}
library(tidyverse)
```



Next, creating the following required vectors:
1. A random sample of size 10 from a uniform[0, 5] distribution
2. A logical vector indicating whether elements of the sample are greater than 2
3. A (length-10) character vector
4. A (length-10) factor vector

```{r vectors}
problem1_df = tibble(
  sample = runif(10, min = 0, max = 5),
  vec_logical = sample > 2,
  vec_char = c("Kao","Shi","Xin","Chun","Ge","Yong","Yuan","Bu","Gua","Ke"),
  vec_factor = factor(c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"))
)
```


For each vector, get the means:

```{r get_means}
#Here is the mean of the sample
mean(problem1_df$sample)

#Here is the mean for logical vector
mean(problem1_df$vec_logical)

#Here is the mean for character vector
mean(problem1_df$vec_char)

#Here is the mean for factor vector
mean(problem1_df$vec_factor)

```
From the above, I tried to take the mean of each variable in my dataframe. What works and what doesn’t? My answer to this question: Only for numeric and logical vectors, we can obtain means using "mean()" this function, but not for character and factor vectors. Note that logical vectors use "1" to denote TRUE, and "0" to denote FALSE, therefore can produce mean value.

Write a code chunk that applies the as.numeric function to the logical, character, and factor variables
```{r as_numeric, eval = FALSE}
convert_veclog = as.numeric(problem1_df$vec_logical)
convert_vecchar = as.numeric(problem1_df$vec_char)
convert_vecfact = as.numeric(problem1_df$vec_factor)
```

What happens?

My answer is: Logical, and factor variables can be converted to numeric vectors, while in contrast, character variable/vector can not be converted to numeric vector. "NA" occurs in this converting character to numeric process.




In a second code chunk, convert your character variable from character to factor to numeric; similarly, convert your factor variable from factor to character to numeric. 

```{r convertions}
#convert your character variable from character to factor to numeric
facconvert_vecchar = as.factor(problem1_df$vec_char)
numconvert_vecchar = as.numeric(facconvert_vecchar)

#convert your factor variable from factor to character to numeric
charconvert_vecfac = as.character(problem1_df$vec_factor)
numconvert_vecfac = as.numeric(charconvert_vecfac)
```

What happens?

My answer is: Character variable to factor to numeric can be converted/proceed successfully; However, converting factor variable to character to numeric did not work well comparing to the process above, since "NA" appears in this process when checking the numeric results.


#Problem 2

Create a data frame comprised of:
1. x: a random sample of size 1000 from a standard Normal distribution
2. y: a random sample of size 1000 from a standard Normal distribution
3. A logical vector indicating whether the x + y > 0
4. A numeric vector created by coercing the above logical vector
5. A factor vector created by coercing the above logical vector

```{r generating_vectors}
set.seed(2)
problem2_df = tibble(
  x = rnorm(1000, sd = 1),
  y = rnorm(1000, sd = 1),
  veclogical_checkxy = x + y > 0,
  numvec_checkxy = as.numeric(veclogical_checkxy),
  facvec_checkxy = as.factor(veclogical_checkxy)
)
```


* The size of the dataset is `r nrow(problem2_df)` rows and `r ncol(problem2_df)` columns.

* The mean of x is `r mean(problem2_df$x)`.

* The median of x is `r median(problem2_df$x)`.

* The proportion of cases for which the logical vector is TRUE equals to `r table(problem2_df$veclogical_checkxy) ["TRUE"]/length(problem2_df$veclogical_checkxy)`.



Make a scatterplot of y vs x
```{r scatter_plot}

ggplot(problem2_df, aes(x = x, y = y, color = veclogical_checkxy)) + geom_point()
```
```{r scatter_plot2}
ggplot(problem2_df, aes(x = x, y = y, color = facvec_checkxy)) + geom_point()
```

```{r scatter_plot3}
ggplot(problem2_df, aes(x = x, y = y, color = numvec_checkxy)) + geom_point()
```