---
title: "p8105_hw1_mm5354"
author: "Mengran Ma"
date: "2018/9/13"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Problem 1

```{r include=FALSE}
library(tidyverse)
```


Here's a **code chunk** that samples from 
a _uniform distribution_:

```{r uniform_sample}
sample = runif(10, min=0, max=5)
```
I can take the mean of the sample, too!
The mean is `r mean(sample)`.

Next, creating the following required vectors:
1. A logical vector indicating whether elements of the sample are greater than 2
2. A (length-10) character vector
3. A (length-10) factor vector

```{r vectors}
vec_logical = sample > 2
vec_char = c("Kao","Shi","Xin","Chun","Ge","Yong","Yuan","Bu","Gua","Ke")
vec_factor = factor(c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"))
```


For each vector, get the means:
Here is the mean for logical vector: `r mean(vec_logical)`

Here is the mean for character vector: `r mean(vec_char)`

Here is the mean for factor vector: `r mean(vec_factor)`

Write a code chunk that applies the as.numeric function to the logical, character, and factor variables
```{r as_numeric}
convert_veclog = as.numeric(vec_logical)
convert_vecchar = as.numeric(vec_char)
convert_vecfact = as.numeric(vec_factor)
```

What happens?

My answer is: "NA" occurs in these processes.

In a second code chunk, convert your character variable from character to factor to numeric; similarly, convert your factor variable from factor to character to numeric. 

```{r convertions}
facconvert_vecchar = as.factor(vec_char)
numconvert_vecchar = as.numeric(facconvert_vecchar)

charconvert_vecfac = as.character(vec_factor)
numconvert_vecfac = as.numeric(charconvert_vecfac)
```


What happens?

My answer is: "NA" occurs in these processes.



